\section{Background Theories}

The scope of this project is to generate customisable solutions that connect vendors and customers by managing and displaying special offers and discounts. The specific product or service segments regard only the systems resulted from the generation process. However, as all aim to provide similar software platforms, there are resemblances in terms of the overall scope and customer interaction method. In order to understand the need for such a retail system, the targeted market segment requires to be analysed.\\

Retail systems have already started taking interest in mobile solutions for more than seven years, aiming to take advantage of their technological expansion through advertising, information gathering and targeting promotions\cite{GREWAL2011S43}. However, the main reason that mobile retail solutions offer is given by the very nature of the device. Being a portable and personal object, these devices have a much more important role than just telecommunications. Providing the means of both organising every aspect of every day life and a portal towards social interaction and media, the mobile devices are in constant use, thus providing large scope for the retail market\cite{SHANKAR2010111}.\\

These factors are proven by the large increase in the percentage of time spent for retail purposes on mobile devices in contrast to desktop platforms. Whereas in 2013 the time spent on mobiles for retail purposes was 46\% and 54\% on desktop\cite{statistic_2017}, the percentage in 2017 has increased in favour of mobile devices with 18\%, reaching 64\%\cite{richter_2017}, thus outbalancing the scale and becoming the main medium for retail purposes. As a result, in addition to the vast applicability of the customisable software platforms, the market segment proves to be very favourable.\\

The previous analysis has shown that the retail market segment has been positively affected by the impact of web and mobile applications expansion. Due to the advancements in mobile technologies and the devices miniaturisation, the range of software solutions has expanded, encompassing almost all social domains. Although simplistic in comparison to industrial systems, mobile applications have reached high levels of profitability and allow the centralisation of data on remote platforms, where it is processed and conveyed in a seamless manner to the users.\\
One such existing software solution is the 'Too Good To Go'\cite{too_good_to_go} mobile application, which targets restaurants and taverns that are legally required to throw away excess food at the end of the day, providing a platform through which customers can purchase the leftovers at very low prices. This benefits both the customers and the restaurants by increasing sales, offering cheap food alternatives and reducing the great amount of thrown away products. Even though 'Too Good To Go' targets only unsold food, it has shown great business value, expanding from only a London targeted application to over 10 European cities. The great success of this application is the main incentive for this project's target, this being but one of numerous niche segments that benefit from the design of such a software platform. The rest of the markets will be more easily available using this project's customisable retail system.\\
Their solution consists of both Android and iOS mobile applications, which display the offers either in the form of a table or a map based on proximity and stock. Category based filtering of the restaurants has also been featured in a recent update of their mobile solutions. The customers have the option of instant buyout for any specific offer and can only redeem it at the restaurant between closing hours. Another functionality of this mobile application is the storage of credit card details for more seamless transactions, as well as increased security. In addition, it offers the possibility to rate previous experiences for other customers' future reference. The system does not present many functionalities, as it is focused on the scope and providing a simple and quick mobile solution.\\

The 'Appsmakerstore'\cite{appsmakerstore} system is a web platform that provides the means to create a customisable retail mobile application for both the iOS and the Android mobile operating systems. Even though its does not target vendors based upon specific types of products or services, its relevance derives from the feature of deploying mobile software solutions only by using functionalities filtering systems and a graphical interface for the clients. This is similar to this project's solution, the only differences being the overview design of the generated mobile applications and the list of functionalities that the client can choose from.\\
As the 'Appsmakerstore''s generated applications fall under the retail category, they provide targeted functionalities from which the clients choose for their tailored applications. The list includes displaying the available products, managing the customer's shopping cart, real-time order and requests processing, displaying promotions, photo galleries, push notifications and loyalty systems. In addition, one of the more interesting features is geolocation alert messaging that has the scope to attract customers when they are in the proximity of venues.\\
The system also allows their clients to manage and update the mobile applications' content remotely, further enhancing the possibilities of seamless customisation. However, this feature is possible through the 'Appsmakerstore''s hosting and maintenance package, through which they are the ones who publish the clients' solutions to the AppStore and Google Play. However useful this option is, this project's system aims to generate the software solutions and to offer the clients complete control over their product.